---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# ALS_clinical_trials

<!-- badges: start -->
<!-- badges: end -->

The goal of ALS_clinical_trials is to ...

```{r packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(patchwork)
```



# Re-use data from our manuscript

This is a brief R tutorial on how to work with the data from our paper.

Read in the data (download from the *data* directory above, or from the 
supplement of our paper):
```{r message=FALSE, warning=FALSE}
timepoints <- read_csv( "https://raw.githubusercontent.com/FelixTheStudent/ALS_clinical_trials/main/data/data_timepoints.csv")
patients <- read_csv( "https://raw.githubusercontent.com/FelixTheStudent/ALS_clinical_trials/main/data/data_patientInfo.csv" )
```


```{r score_over_time, echo = FALSE}
df <- timepoints %>% filter(patient == "p109")
df %>% ggplot(aes(time, ALSFRSR))+geom_point() + ylim(c(0, 60)) + 
df %>% ggplot(aes(time, nfl))    +geom_point() + scale_y_log10(limits=c(1,1500))
```


# Notes

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.